\documentclass[12pt, letterpaper]{article}

\usepackage[T1]{fontenc}
\usepackage{palatino}
\usepackage[top=0.85in, bottom=1in, left=1in, right=1in, headheight=14pt]{geometry}
\usepackage{fancyhdr}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{array}
\usepackage{tabularx}
\usepackage{microtype}
\usepackage{titlesec}

% Running header: name left, page number right, no rule
\pagestyle{fancy}
\fancyhf{}
\fancyhead[L]{\textit{Yi-Wen (Penny) Chen}}
\fancyhead[R]{\thepage}
\renewcommand{\headrulewidth}{0pt}

% First page: no header
\fancypagestyle{firstpage}{%
  \fancyhf{}%
  \renewcommand{\headrulewidth}{0pt}%
}

% Section headings: bold, large, with rule beneath
\titleformat{\section}
  {\large\bfseries}
  {}{0em}{}
  [\vspace{2pt}\hrule\vspace{0pt}]
\titlespacing*{\section}{0pt}{14pt}{8pt}

\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}

% Subsection heading within cvblock
\newcommand{\cvsubsection}[1]{\vspace{6pt}\noindent{\bfseries #1}}

% Indented content block (mirrors David Huang's indented sections)
\newenvironment{cvblock}{%
  \begin{list}{}{%
    \setlength{\leftmargin}{0.35in}%
    \setlength{\rightmargin}{0pt}%
    \setlength{\topsep}{2pt}%
    \setlength{\parsep}{0pt}%
    \setlength{\itemsep}{0pt}%
    \setlength{\partopsep}{0pt}%
  }%
  \item[]%
}{%
  \end{list}%
}

%-------------------------------------------
\begin{document}
\thispagestyle{firstpage}

%---- NAME + LAST UPDATED ----
\begin{minipage}[b]{0.70\textwidth}
{\LARGE\bfseries Yi-Wen (Penny) Chen}
\end{minipage}%
\hfill
\begin{minipage}[b]{0.28\textwidth}\raggedleft
\footnotesize Last updated: June 2026
\end{minipage}

\vspace{16pt}

%---- CONTACT ----
\begin{minipage}[t]{0.55\textwidth}
Marketing Division\\
Columbia Business School\\
3022 Broadway, New York, NY 10027
\end{minipage}%
\hfill
\begin{minipage}[t]{0.40\textwidth}\raggedright
\href{mailto:YChen26@gsb.columbia.edu}{YChen26@gsb.columbia.edu}\\[2pt]
\href{https://ywchen82.github.io}{ywchen82.github.io}
\end{minipage}

\vspace{4pt}

%---- EDUCATION ----
\section{Education}
\begin{cvblock}
\textbf{Columbia Business School}, New York, NY, USA\\
Ph.D., Marketing, 2021--2027 (expected).\\
M.Phil., 2024.

\medskip
\textbf{National Taiwan University}, Taipei, Taiwan\\
M.A., Economics, 2019.

\medskip
\textbf{National Taiwan University}, Taipei, Taiwan\\
LL.B., Law, Minor in Political Science (International Relation Track), 2016.
\end{cvblock}

%---- RESEARCH INTERESTS ----
\section{Research Interests}
\begin{cvblock}
\textbf{Substantive:} Targeting and Personalization, Influencer and Creator Economy\\[4pt]
\textbf{Methodology:} Machine Learning, Causal Inference, Optimization, Game Theory
\end{cvblock}

%---- WORKING PAPERS ----
\section{Working Papers}
\begin{enumerate}[leftmargin=0.55in, label=\arabic*., itemsep=10pt, topsep=4pt, parsep=0pt]

\item \textbf{Targeting with Operational Constraints.}\\
Yi-Wen Chen, George Gui, and Eva Ascarza.\\
\textit{Job Market Paper.}

\item \textbf{Policy-Aware Sampling: Prioritizing Consequential Customers for Optimized Targeting Policies.}\\
Yi-Wen Chen, Eva Ascarza, and Oded Netzer.\\
Conditionally Accepted at \textit{Journal of Marketing Research}.

\item \textbf{Dual Monetization on Creator Platforms: The Interplay Between Advertising Revenue and Brand Sponsorship.}\\
Yi-Wen Chen and Kinshuk Jerath.

\end{enumerate}

%---- WORK IN PROGRESS ----
\section{Selected Work in Progress}
\begin{enumerate}[leftmargin=0.55in, label=\arabic*., itemsep=10pt, topsep=4pt, parsep=0pt]

\item\textbf{Adaptive Targeting in a Customer Changing Environment.}\\
Hengxu Lin, Yi-Wen Chen, and Oded Netzer.

\end{enumerate}

%---- HONORS AND AWARDS ----
\newpage
\section{Honors and Awards}
\begin{cvblock}
Government Scholarships for Study Abroad (GSSA), Ministry of Education, Taiwan, 2025--2027.

\smallskip
ISMS Marketing Science Doctoral Consortium Fellow, 2025.

\smallskip
Luxury Education Foundation Awards, Columbia Business School, 2024.

\smallskip
Deming Center Doctoral Fellowship, Columbia Business School, 2024.

\smallskip
Columbia Business School Doctoral Fellowship, 2021--2026.

\smallskip
Dean's List, National Taiwan University, Fall 2012, Fall 2013.
\end{cvblock}

%---- CONFERENCE PRESENTATIONS ----
\section{Conference Presentations}
\begin{cvblock}
\textbf{2026:} ISMS Marketing Science Conference.

\smallskip
\textbf{2025:} Conference on Artificial Intelligence, Machine Learning, and Business Analytics;
Platform Doctoral Symposium; ISMS Marketing Science Conference;
University of Houston Doctoral Symposium.

\smallskip
\textbf{2024:} Conference on Digital Experimentation (CODE@MIT).
\end{cvblock}

%---- TEACHING EXPERIENCE ----
\section{Teaching Experience}
\begin{cvblock}
\cvsubsection{Columbia Business School} --- Teaching Assistant

\vspace{4pt}
\begin{tabularx}{\linewidth}{Xr}
Analytical Models (PhD) & Spring 2025 \\
Empirical Models (PhD) & Spring 2025 \\
Marketing Analytics & Fall 2024, Fall 2025 \\
Digital Marketing & Fall 2022 \\
Statistical Modeling and Decision Making & Fall 2022 \\
Pricing Strategy & Spring 2022, Spring 2023 \\
\end{tabularx}

\cvsubsection{National Taiwan University} --- Teaching Assistant

\vspace{4pt}
\begin{tabularx}{\linewidth}{Xr}
Applied Statistics & Fall 2016--Spring 2018 \\
\end{tabularx}
\end{cvblock}

%---- INDUSTRY EXPERIENCE ----
\section{Industry Experience}
\begin{cvblock}
\textbf{Sinopac Securities Asia}, Data Scientist, 2019--2020.
\end{cvblock}

%---- PHD COURSEWORK ----
\newpage
\section{PhD Coursework}
\begin{cvblock}
\cvsubsection{Marketing, Columbia Business School}

\vspace{4pt}
\begin{tabularx}{\linewidth}{Xr}
Empirical Models & Oded Netzer \\
Mathematical Models in Marketing & Rajeev Kohli \\
Analytical Models & Kinshuk Jerath \\
Consumer Behavior I & Michel Pham \& Bernd Schmitt \\
Consumer Behavior II & Eric Johnson \\
Marketing, Decisions, and Methods & Don Lehmann \\
Bayesian Computation and Modeling & Asim Ansari \\
Applied Multivariate Statistics & Kamel Jedidi \\
\end{tabularx}

\cvsubsection{Economics, Columbia University}

\vspace{4pt}
\begin{tabularx}{\linewidth}{Xr}
Introduction to Econometrics I & Joss Montiel Olea \& Sok Lee \\
Introduction to Econometrics II & Serena Ng \& Bernard Salanie \\
Econometrics IV & Sok Lee \\
Economic Analysis I, II & Geoffrey Heal \\
Industrial Organization I & Gautam Gowrisankaran \\
Industrial Organization II & Pietro Tebaldi \\
\end{tabularx}

\cvsubsection{Economics, National Taiwan University}

\vspace{4pt}
\begin{tabularx}{\linewidth}{Xr}
Econometric Theory & Yi-Ting Chen \\
Microeconomic Theory & Hendrick Rommeswinkel \& Po-Han Fong \\
Macroeconomic Theory & Yi-Chan Tsai \& Pei-Ju Liao \\
Applied Microeconomics I, II & Ming-Jen Lin \\
\end{tabularx}

\cvsubsection{Statistics and Computer Science, Columbia University}

\vspace{4pt}
\begin{tabularx}{\linewidth}{Xr}
Applied Causality & David Blei \\
Foundation of Graphical Models (Probabilistic Machine Learning) & David Blei \\
\end{tabularx}
\end{cvblock}

%---- SKILLS ----
\section{Skills}
\begin{cvblock}
\textbf{Programming:} Python, R, Mathematica, SQL, STATA, Stan\\[4pt]
\textbf{Languages:} Mandarin (Native), English (Fluent)
\end{cvblock}

%---- REFERENCES ----
\newpage
\section{References}
\begin{cvblock}
\begin{minipage}[t]{0.46\textwidth}
\textbf{Oded Netzer} (Co-advisor)\\
Arthur J. Samberg Professor of Business\\
Columbia University\\
\href{mailto:onetzer@gsb.columbia.edu}{onetzer@gsb.columbia.edu}
\end{minipage}%
\hfill
\begin{minipage}[t]{0.46\textwidth}
\textbf{George Gui} (Co-advisor)\\
Assistant Professor of Marketing\\
Columbia University\\
\href{mailto:zg2467@gsb.columbia.edu}{zg2467@gsb.columbia.edu}
\end{minipage}

\vspace{1em}

\begin{minipage}[t]{0.46\textwidth}
\textbf{Eva Ascarza}\\
Professor of Business Administration\\
Harvard University\\
\href{mailto:eascarza@hbs.edu}{eascarza@hbs.edu}
\end{minipage}%
\hfill
\begin{minipage}[t]{0.46\textwidth}
\textbf{Kinshuk Jerath}\\
Arthur F. Burns Professor of Free and Competitive Enterprise\\
Columbia University\\
\href{mailto:kj2323@columbia.edu}{kj2323@columbia.edu}
\end{minipage}
\end{cvblock}

\end{document}
